Local PCA Shows How the Effect of Population Structure Differs Along the Genome

### 2018-08-10 writeup/local_pca_paper.tex
tidied table

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Wed Feb  8 16:17:12 2017
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & 10000snp, 2 PCs & 1000snp, 2 PCs & 10000snp, 5 PCs & 100000bp, 2 PCs & 10000bp, 2 PCs \\ 
  \hline
10000snp, 2 PCs & 1.00 & 0.87 & 0.96 & 0.90 & 0.88 \\ 
  1000snp, 2 PCs & 0.68 & 1.00 & 0.73 & 0.68 & 0.94 \\ 
  10000snp, 5 PCs & 0.96 & 0.92 & 1.00 & 0.88 & 0.93 \\ 
  100000bp, 2 PCs & 0.90 & 0.87 & 0.88 & 1.00 & 0.87 \\ 
  10000bp, 2 PCs & 0.68 & 0.93 & 0.72 & 0.67 & 1.00 \\ 
   \hline
\end{tabular}
\end{table}

[[2]]
% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Wed Feb  8 16:17:12 2017
\begin{table}[ht]
\centering
    \begin{tabular}{rrrrrr}
      \hline
     MDS1 & 10000 SNPs, 2 PCs & 1000 SNPs, 2 PCs & 10000 SNPs, 5 PCs & 100000bp, 2 PCs & 10000bp, 2 PCs \\ 
      \hline
      10000 SNPs, 2 PCs & 1.00 & 0.54 & 0.93 & 0.87 & 0.56 \\ 
      1000 SNPs, 2 PCs & 0.82 & 1.00 & 0.76 & 0.83 & 0.92 \\ 
      10000 SNPs, 5 PCs & 0.93 & 0.50 & 1.00 & 0.83 & 0.52 \\ 
      100000bp, 2 PCs & 0.87 & 0.59 & 0.84 & 1.00 & 0.58 \\ 
      10000bp, 2 PCs & 0.83 & 0.92 & 0.77 & 0.84 & 1.00 \\ 
       \hline
    \end{tabular}
    \begin{tabular}{rrrrrr}
      \hline
     MDS2 & 10000snp, 2 PCs & 1000snp, 2 PCs & 10000snp, 5 PCs & 100000bp, 2 PCs & 10000bp, 2 PCs \\ 
      \hline
      10000snp, 2 PCs & 1.00 & 0.54 & 0.93 & 0.87 & 0.56 \\ 
      1000snp, 2 PCs & 0.82 & 1.00 & 0.76 & 0.83 & 0.92 \\ 
      10000snp, 5 PCs & 0.93 & 0.50 & 1.00 & 0.83 & 0.52 \\ 
      100000bp, 2 PCs & 0.87 & 0.59 & 0.84 & 1.00 & 0.58 \\ 
      10000bp, 2 PCs & 0.83 & 0.92 & 0.77 & 0.84 & 1.00 \\ 
       \hline
    \end{tabular}
    \begin{caption}
        Correlations between MDS coordinates of genomic regions
        between runs with different parameter values.
        To produce these, 
        we first ran the algorithm with the specified window size and number of PCs 
        ($k$ in equation \plr{XXX})
        on the full \textit{Medicago truncatula} dataset.
        Then to obtain the correlation between results obtained from parameters A in the row of the matrix above
        and parameters B in the column of the matrix above,
        we mapped the windows of B to those of A by averaging MDS coordinates of any windows of B whose midpoints lay in the corresponding window of A;
        we then computed the correlation between the MDS coordinates of A and the averaged MDS coordinates of B.
        This is not a symmetric operation, so these matrices are not symmetric.
        As expected, parameter values with smaller windows produce noisier estimates.
        Plots of MDS values along the genome are visually nearly identical
        for parameter sets having similar window sizes --
        full reports are available as supplementary material on Data Dryad \plr{XXX}.
        \label{tab:param_cors}
    \end{caption}
\end{table}

>>>>

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Wed Feb  8 16:17:12 2017
\begin{table}[ht]
\centering
    \begin{tabular}{rrrrrr}
      \hline
          & 10000 SNPs & 1000 SNPs & 10000 SNPs & 100000bp & 10000bp \\ 
     MDS1 & 2 PCs & 2 PCs & 5 PCs & 2 PCs & 2 PCs \\ 
      \hline
  10000 SNPs, 2 PCs & 1.00 & 0.87 & 0.96 & 0.90 & 0.88 \\ 
  1000 SNPs, 2 PCs & 0.68 & 1.00 & 0.73 & 0.68 & 0.94 \\ 
  10000 SNPs, 5 PCs & 0.96 & 0.92 & 1.00 & 0.88 & 0.93 \\ 
  100000bp, 2 PCs & 0.90 & 0.87 & 0.88 & 1.00 & 0.87 \\ 
  10000bp, 2 PCs & 0.68 & 0.93 & 0.72 & 0.67 & 1.00 \\ 
       \hline
       \hline
        MDS2 & &&&&\\
      \hline
      10000 SNPs, 2 PCs & 1.00 & 0.54 & 0.93 & 0.87 & 0.56 \\ 
      1000 SNPs, 2 PCs & 0.82 & 1.00 & 0.76 & 0.83 & 0.92 \\ 
      10000 SNPs, 5 PCs & 0.93 & 0.50 & 1.00 & 0.83 & 0.52 \\ 
      100000bp, 2 PCs & 0.87 & 0.59 & 0.84 & 1.00 & 0.58 \\ 
      10000bp, 2 PCs & 0.83 & 0.92 & 0.77 & 0.84 & 1.00 \\ 
       \hline
    \end{tabular}
    \begin{caption}
        Correlations between MDS coordinates of genomic regions
        between runs with different parameter values.
        To produce these, 
        we first ran the algorithm with the specified window size and number of PCs 
        ($k$ in equation \plr{XXX})
        on the full \textit{Medicago truncatula} dataset.
        Then to obtain the correlation between results obtained from parameters A in the row of the matrix above
        and parameters B in the column of the matrix above,
        we mapped the windows of B to those of A by averaging MDS coordinates of any windows of B whose midpoints lay in the corresponding window of A;
        we then computed the correlation between the MDS coordinates of A and the averaged MDS coordinates of B.
        This is not a symmetric operation, so these matrices are not symmetric.
        As expected, parameter values with smaller windows produce noisier estimates.
        Plots of MDS values along the genome are visually nearly identical
        for parameter sets having similar window sizes --
        full reports are available as supplementary material on Data Dryad \plr{XXX}.
        \label{tab:param_cors}
    \end{caption}
\end{table}
